Network Configuration Synthesis with Abstract Topologies

### 2016-11-14 paper/abstraction/paper.tex
clarify metavariables

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policy} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT a & \textit{path preferences}  \\
     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{predicate} \\
     a      &::=& agg(t, r_1 \rightarrow r_2) & \textit{aggregation} \\
     r       &::=& l \BNFALT \emptyset \BNFALT \In \BNFALT \Out \BNFALT r_1 \cup r_2 \BNFALT & \textit{regular path} \\
             &   & r_1 \cap r_2 \BNFALT r_1 \cdot r_2 \BNFALT \NOT r \BNFALT r^* \\
  \end{array} \]%

>>>>

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     d       &\in& \textit{Integers} \\
     x       &\in& \textit{Variables} \\
     pol     &::=& p_1, \dots, p_n & \text{Policy} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m \BNFALT a & \text{Path Preferences}  \\
     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \text{Predicate} \\
     a      &::=& \mathit{agg}(t, r_1 \rightarrow r_2) & \text{Aggregation} \\
     r       &::=& l \BNFALT \emptyset \BNFALT \CD{in} \BNFALT \CD{out} \BNFALT r_1 \cup r_2 \BNFALT & \text{Regular Path} \\
             &   & r_1 \cap r_2 \BNFALT r_1 \cdot r_2 \BNFALT \NOT r \BNFALT r^* \\
  \end{array} \]%
